Simulation Modeling of Glycosylation Effects on Potassium Channels of Mouse Cardiomyocytes

### 2021-06-22 draft_plos.tex
Text and references

\documentclass[journal]{IEEEtran}

%\usepackage[retainorgcmds]{IEEEtrantools}
%\usepackage{bibentry}  
\usepackage{xcolor,soul,framed} %caption

\colorlet{shadecolor}{yellow}
% \usepackage{color,soul}
\usepackage[pdftex]{graphicx}
\graphicspath{{../photo/}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\usepackage[caption=false]{subfig}
\usepackage[cmex10]{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{mdwmath}
\usepackage{mdwtab}
\usepackage{eqparbox}
\usepackage{cite}
\usepackage{tabularx,booktabs}
\usepackage[flushleft]{threeparttable} % table notes
\usepackage{algorithm,algorithmic}
\usepackage{footmisc}
\usepackage[colorlinks=true]{hyperref}
\hypersetup{
    citecolor = black,
    urlcolor = blue
}

\hyphenation{op-tical net-works semi-conduc-tor}

%\bstctlcite{IEEE:BSTcontrol}

% === TITLE & AUTHORS ===================================================
% =======================================================================
\begin{document}
\bstctlcite{IEEEexample:BSTcontrol}
    \title{Simulation Modeling of Glycosylation Effects on Potassium Channels of Mouse Cardiomyocytes}
  \author{Haedong Kim,~\IEEEmembership{{Student Member},~IEEE,}
      Hui Yang,~\IEEEmembership{Senior Member,~IEEE,}
      Andrew R. Ednie,
      and~Eric S. Bennett
  \thanks{Manuscript received Month Day, Year}
  \thanks{H. Kim and H. Yang are with the Complex Systems Monitoring, Modeling, and Control Laboratory, The Pennsylvania State University, University Park, PA 16802 USA (e-mail: huk344@psu.edu; huy25@psu.edu).}% <-this % stops a space
  \thanks{A. R. Ednie and E. S. Bennett are with the Department of Neuroscience, Cell Biology and Physiology, Wright State University, Dayton, OH 45435 USA (e-mail: andrew.ednie@wright.edu; eric.bennett@wright.edu).}}

% The paper headers
% The only time the second header will appear is for the odd numbered pages after the title page when using the two-side option.
\markboth{}%
{Kim \MakeLowercase{\textit{et al.}}: Potassium Channel}

% =======================================================================
\maketitle

% === ABSTRACT ==========================================================
% =======================================================================
\begin{abstract}
Dilated cardiomyopathy (DCM) is the third most common cause of heart failure and the primary reason for heart transplantation; upward of 70\% of DCM cases are considered idiopathic. Our in-vitro experiments showed that reduced hybrid/complex N-glycosylation in mouse cardiomyocytes is linked with DCM. Further, we observed direct effects of reduced N-glycosylation on $\text{K}_{v}$ gating. However, it is difficult to rigorously determine the effects of glycosylation on $\text{K}_{v}$ activity, because there are multiple $\text{K}_{v}$ isoforms in cardiomyocytes. Due to complex functions of $\text{K}_{v}$ isoforms, only the sum of $\text{K}^{+}$ currents ($\text{I}_{Ksum}$) can be recorded experimentally and decomposed later using exponential fitting to estimate component currents such as $\text{I}_{Kto}$, $\text{I}_{Kslow}$, $\text{I}_{Kss}$. However, such estimation cannot adequately describe glycosylation effects and $\text{K}_{v}$ mechanisms. Here, we propose to develop simulation models of $\text{K}_{v}$ kinetics in mouse ventricular myocytes and calibrate their parameters using the in-vitro data under normal and reduced glycosylation conditions through ablation of the Mgat1 gene (i.e., Mgat1KO). Calibrated models facilitate the prediction of $\text{K}_{v}$ characteristics at different voltages that are not directly observed in the in-vitro experiments. A novel calibration procedure is also proposed to tackle nonlinear and high-dimensionality challenges in simulation models. Experimental results show that, in the Mgat1KO group, both $\text{I}_{Kto}$ and $\text{I}_{Kslow}$ densities are shown to be significantly reduced and the rate of $\text{I}_{Kslow}$ inactivation is much slower. The proposed approach has strong potential to couple simulation models with experimental data for gaining a better understanding of glycosylation effects on $\text{K}_{v}$ kinetics.
\end{abstract}

% === KEYWORDS ==========================================================
% =======================================================================
\begin{IEEEkeywords}
Electrophysiology, N-glycosylation, dilated cardiomyopathy, potassium channel, simulation modeling, genetic algorithm. 
\end{IEEEkeywords}

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

% === I. INTRODUCTION ===================================================
% =======================================================================
\section{Introduction}
\IEEEPARstart{H}{eart} disease is the leading cause of death globally, accounting for 23\% of deaths in the U.S. in 2017 \cite{cdc2019deaths}. Dilated cardiomyopathy (DCM) is the third most common cause of heart failure and the most frequent reason for heart transplantation \cite{weintraub2017dilated}. DCM is characterized by enlarged and weakened ventricular chambers, and it is associated with systolic and contractile dysfunction that has a high risk to heart failure, with approximately 70\% of DCM cases regarded as idiopathic \cite{weintraub2017dilated, lakdawala2013dilated, hershberger2011update}. There has been consistent and increasing evidence of a link between aberrant glycosylation and heart failure \cite{gehrmann2003cardiomyopathy, footitt2009cardiomyopathy, marques2017cardiac}. Recently, we showed that reduction of hybrid/complex N-glycosylation in mouse cardiomyocytes, through ablation of the Mgat1\footnote{Mannosyl ($\alpha$-1,3-)-Glycoprotein $\beta$-1,2-N-acetylglucosaminyltransferase} gene that encodes a critical glycosyltransferase (GlcNAcT1\footnote{UDP-GlcNAc:$\alpha$-3-D-mannoside-$\beta$1,2-N-acetylglucosaminyltransferase}) (Mgat1KO model), is sufficient to cause DCM \cite{ednie2019reduced, ednie2019reduced2}. Mgat1KO mice develop DCM, heart failure, and 100\% die early, likely from ventricular arrhythmias resulting in sudden cardiac death. Further, Mgat1KO ventricular myocytes demonstrated altered electromechanical functions, including excitation-contraction (EC) coupling, are consistent with observed changes in electrical signaling caused by acute and downstream (disease-related) effects on voltage-gated ion channel (VGIC) gating and activity \cite{ednie2019reduced}.

Thus, we investigated the impact of reduced hybrid/complex N-glycosylation through the lens of electrophysiology. Electrophysiology refers to studies of electrical properties in scales from ion channels in cells to organ systems \cite{scanziani2009electrophysiology}. Electrical signaling in the heart has vital functions related to intra and extracellular communication, rhythmicity of heartbeats, and provides a driving force for contraction. The action potential (AP) is the net transmembrane potential varying over time which results from the composite activities of different ion channels \cite{grant2009cardiac}. Fig. 1-(a) shows the simulated AP of a mouse ventricular apex myocyte using models adopted from \cite{bondarenko2004computer}. The AP is the result of orchestrated activities of various ionic currents described in Fig. 1-(b). Even small changes in VGIC function can contribute to aberrant AP waveform and/or conduction, leading to arrhythmias. As illustrated in Fig. 2, $\text{Na}^{+}$ channels ($\text{Na}_{v}$) are responsible for AP initiation, or the depolarization phase, $\text{Ca}^{2+}$ channels ($\text{Ca}_{v}$) drive the prolonged depolarization phase particularly in larger species (“plateau”), while several $\text{K}^{+}$ channel ($\text{K}_{v}$) isoforms are collectively responsible for AP deactivation, i.e., repolarization. Like most transmembrane proteins, VGICs are heavily glycosylated membrane proteins \cite{ednie2011modulation}. Studies have proven that glycosylation can affect VGIC function predominantly. For example, we reported that a saturating, electrostatic effect of negatively charged sialic acids, which are typically attached to the terminal of glycan branches, significantly altered cardiac electrical signaling \cite{ednie2013expression, ednie2015reduced}. Our recent studies observed aberrant electrical signaling, e.g., prolonged APs and abnormal early re-activations, in Mgat1KO ventricular apex myocytes \cite{ednie2019reduced, ednie2019reduced2}. These observations strongly support direct and disease-related effects of reduced N-glycosylation on VGIC gating and activity.
\begin{figure}
    \label{fig1}
    \centering
    \subfloat[]{\includegraphics[width=0.8\linewidth]{photo/sim_ap.png}}
    \\
    \subfloat[]{\includegraphics[width=0.8\linewidth]{photo/sim_currents.png}}
    \caption{Simulation results of the (a) action potential and (b) relevant ionic currents (i.e., $\text{I}_{Kto}$, $\text{I}_{Kslow}$, $\text{I}_{Kss}$, $\text{I}_{Na}$, and $\text{I}_{CaL}$) of mouse ventricular myocytes. Potassium currents have positive currents, while sodium and calcium currents are negative.}
\end{figure}

\begin{figure}
    \label{fig2}
    \centering
    \includegraphics[width=0.8\linewidth]{photo/ap_ion_channels.png}
    \caption{Predominant ion channels in human ventricular myocytes and their functional role in shaping an AP.}
    \label{fig:my_label}
\end{figure}

@@

Therefore, this paper presents simulation modeling of dominant $\text{K}^{+}$ currents in mouse ventricular myocytes and further calibrate their parameters using the in-vitro data under normal and reduced glycosylation conditions through ablation of the Mgat1 gene. Specifically, we propose an optimization procedure to calibrate simulation models of potassium channel isoform activity, $\text{I}_{Kto}$ and $\text{I}_{Kslow}$, in mouse cardiomyocytes.  Fig. 3 shows  major component $\text{K}^{+}$ currents, including $\text{I}_{Ksum}$, $\text{I}_{Kto}$, $\text{I}_{Kslow}$ and $\text{I}_{Kss}$. Key statistics of component currents, amplitudes, and inactivation rates ($\tau$'s) are measured from in-vitro experimental data with a 4.5 s voltage-clamp protocol (see details in Section III). The major contributions of this paper are summarized as follows.
\begin{itemize}
    \item Simulation models are integrated with in-vitro experiments to investigate the effects of reduced N-glycosylation on $\text{K}_{v}$ activity of mouse myocytes. Computer simulation helps demonstrate the voltage-gating mechanism and conductance kinetics that cannot be readily available through traditional exponential fitting. 
    \item A self-breeding Genetic Algorithm procedure is developed to calibrate simulation models of voltage-gated $\text{K}^{+}$ channel of mouse ventricular apex myocytes based on key characterisitcs and raw data obtained from in-vitro experiments.
    \item Calibrated models facilitate the prediction of $\text{K}_{v}$ characteristics at different voltages that are not observed in the in-vitro experiments. In the Mgat1KO group, both $\text{I}_{Kto}$ and $\text{I}_{Kslow}$ densities are shown to be significantly reduced and the rate of $\text{I}_{Kslow}$ inactivation is much slower.
    \item Simulation modeling of cardiac myocytes is conducive to gain a better understanding of detailed $\text{K}_{v}$ kinetics, as well as how reduced glycosylation through ablation of Mgat1 gene impacts $\text{K}_{v}$ kinetics.
\end{itemize}

% === II. RESEARCH BACKGROUND ===========================================
% =======================================================================
\section{Research Background}
\subsection{Glycosylation and DCM}
Protein glycosylation is an essential cellular process that impacts many cell functions \cite{marques2017cardiac}. Briefly, protein glycosylation is the sequential co-/post-translational process of attaching sugar residues (glycans) to proteins. Cardiac VGICs are heavily glycosylated proteins with upwards of 30\% of their mass consisting of N- and O-linked glycans. A growing number of cardiac diseases, including DCM and hypertrophic cardiomyopathy, can present with concurrent, albeit, modest changes in glycosylation \cite{gehrmann2003cardiomyopathy, footitt2009cardiomyopathy, marques2017cardiac}. Mgat1 expression was implicated in cardiac function and shown to be down-regulated in human end-stage idiopathic DCM. Genome-wide searches identified changes in glycosylation-related gene expression in human idiopathic DCM, including glycosyltransferases \cite{barrans2002global, hwang2002microarray, yung2004gene}; and proteomic/glycomic studies show changes in serum N-glycosylation in heart disease models and in humans with DCM risk factors \cite{nishio1995identification, knezevic2009variability, miura2016glycomics, nagai2016aberrant, yang2015glycoproteins}. Models of DCM/heart failure were associated with subtle changes in glycosylation of proteins involved in electromechanical processes, and ~20\% of patients with congenital disorders of glycosylation (CDG) present with cardiac deficits, including idiopathic DCM \cite{gehrmann2003cardiomyopathy, marques2017cardiac}. The data suggest a correlation between modest changes in extracellularly facing glycosylation and DCM/heart disease.

\subsection{Simulation Modeling of Mouse Ventricular Myocytes}
Electrophysiology was pioneered by Hodgkin and Huxley with a series of well-known experiments on the squid giant axon \cite{hodgkin1952quantitative}. Their simulation model was built upon two fundamental principles observed in the experimental data. 1) Cells are selectively activated by different ion channels. 2) Activities of ion channels to produce ionic currents are controlled through voltage changes, from which the name ``voltage-gated ion channels'' originates. The voltage-gating mechanism is encoded in the simulations model with partial differential equations. Not only are simulation models compatible with data and descriptive, but they also simulate changes of AP waveforms and ion channel activity. Thus, models provide connections among ionic currents, action potentials, and disease effects. However, significant domain knowledge and in-vitro investigations are required, because simulation models often have complex structures based on nonlinear functions and differential equations with a high-dimensional set of parameters.

@@

\subsection{$\text{K}_{v}$ Isoforms}
\begin{figure}
    \label{fig3}
    \centering
    \includegraphics[width=0.8\linewidth]{photo/k_decomp_eg.png}
    \caption{Example of $\text{K}^{+}$ current decomposition into three component currents. Each component $\text{K}^{+}$ current has different characteristics in terms of their peak and decaying phase.}
\end{figure}
The orchestrated activity of different $\text{K}_{v}$ isoforms produces multiple component currents, as illustrated in Fig. 1-(b) and Fig. 3. However, it is difficult to rigorously delineate the multiple component $\text{K}^{+}$ currents through voltage-clamp experiments alone because only the sum of $\text{K}^{+}$ currents is measured and recorded. Thus, $\text{I}_{Ksum}$ is usually decomposed mathematically by fitting the peak and decaying portion of each component current trace with an exponential function \cite{brunet2004heterogeneous}. As given in Equation (1), a standard exponential function has three parameters: amplitude ($\text{A}$), time constant ($\tau$), and constant offset value $\text{C}$. $t$ is time in millisecond. Amplitude refers to the value of the peak and $\tau$ to the time constant when current reduces by $e^{-1}$ (~63\%) of the peak.

>>>>

% Template for PLoS
% Version 3.5 March 2018
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file 
% and leave only the final text of your manuscript. 
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8x]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}

% algorithm table
\usepackage{algorithm,algorithmic}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\cline{#1}%
\noalign{\vskip\arrayrulewidth}%
\noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Simulation modeling of glycosylation effects on potassium channels of mouse cardiomyocytes} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Haedong Kim \textsuperscript{1},
Hui Yang \textsuperscript{1*},
Andrew R. Ednie \textsuperscript{2},
Eric S. Bennett \textsuperscript{2}
\\
\bigskip
\textbf{1} Complex Systems Monitoring, Modeling, and Control Laboratory, The Pennsylvania State University, University Park, Pennsylvania, United States of America
\\
\textbf{2} Department of Neuroscience, Cell Biology and Physiology, Wright State University, Dayton, Ohio, United States of America
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
% \Yinyang These authors contributed equally to this work.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
% \ddag These authors also contributed equally to this work.

% Current address notes
% \textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
% \textcurrency b Insert second current address 
% \textcurrency c Insert third current address

% Deceased author note
% \dag Deceased

% Group/Consortium Author Note
% \textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* huiyang@psu.edu

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Dilated cardiomyopathy (DCM) is the third most common cause of heart failure and the primary reason for heart transplantation; upward of 70\% of DCM cases are considered idiopathic. Our in-vitro experiments showed that reduced hybrid/complex N-glycosylation in mouse cardiomyocytes is linked with DCM. Further, we observed direct effects of reduced N-glycosylation on $\text{K}_{v}$ gating. However, it is difficult to rigorously determine the effects of glycosylation on $\text{K}_{v}$ activity, because there are multiple $\text{K}_{v}$ isoforms in cardiomyocytes. Due to complex functions of $\text{K}_{v}$ isoforms, only the sum of $\text{K}^{+}$ currents ($\text{I}_{Ksum}$) can be recorded experimentally and decomposed later using exponential fitting to estimate component currents such as $\text{I}_{Kto}$, $\text{I}_{Kslow}$, $\text{I}_{Kss}$. However, such estimation cannot adequately describe glycosylation effects and $\text{K}_{v}$ mechanisms. Here, we propose to develop simulation models of $\text{K}_{v}$ kinetics in mouse ventricular myocytes and calibrate their parameters using the in-vitro data under normal and reduced glycosylation conditions through ablation of the Mgat1 gene (i.e., Mgat1KO). Calibrated models facilitate the prediction of $\text{K}_{v}$ characteristics at different voltages that are not directly observed in the in-vitro experiments. A novel calibration procedure is also proposed to tackle nonlinear and high-dimensionality challenges in simulation models. Experimental results show that, in the Mgat1KO group, both $\text{I}_{Kto}$ and $\text{I}_{Kslow}$ densities are shown to be significantly reduced and the rate of $\text{I}_{Kslow}$ inactivation is much slower. The proposed approach has strong potential to couple simulation models with experimental data for gaining a better understanding of glycosylation effects on $\text{K}_{v}$ kinetics.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
% \section*{Author summary}
% Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

\linenumbers

% Use "Eq" instead of "Equation" for equation citations.
\section*{Introduction}
% === I. INTRODUCTION ===================================================
% =======================================================================
Heart disease is the leading cause of death globally, accounting for 23\% of deaths in the U.S. in 2017 \cite{cdc2019deaths}. Dilated cardiomyopathy (DCM) is the third most common cause of heart failure and the most frequent reason for heart transplantation \cite{weintraub2017dilated}. DCM is characterized by enlarged and weakened ventricular chambers, and it is associated with systolic and contractile dysfunction that has a high risk to heart failure, with approximately 70\% of DCM cases regarded as idiopathic \cite{weintraub2017dilated, lakdawala2013dilated, hershberger2011update}. There has been consistent and increasing evidence of a link between aberrant glycosylation and heart failure \cite{gehrmann2003cardiomyopathy, footitt2009cardiomyopathy, marques2017cardiac}. Recently, we showed that reduction of hybrid/complex N-glycosylation in mouse cardiomyocytes, through ablation of the Mgat1\footnote{Mannosyl ($\alpha$-1,3-)-Glycoprotein $\beta$-1,2-N-acetylglucosaminyltransferase} gene that encodes a critical glycosyltransferase (GlcNAcT1\footnote{UDP-GlcNAc:$\alpha$-3-D-mannoside-$\beta$1,2-N-acetylglucosaminyltransferase}) (Mgat1KO model), is sufficient to cause DCM \cite{ednie2019reduced, ednie2019reduced2}. Mgat1KO mice develop DCM, heart failure, and 100\% die early, likely from ventricular arrhythmias resulting in sudden cardiac death. Further, Mgat1KO ventricular myocytes demonstrated altered electromechanical functions, including excitation-contraction (EC) coupling, are consistent with observed changes in electrical signaling caused by acute and downstream (disease-related) effects on voltage-gated ion channel (VGIC) gating and activity \cite{ednie2019reduced}.

Thus, we investigated the impact of reduced hybrid/complex N-glycosylation through the lens of electrophysiology. Electrophysiology refers to studies of electrical properties in scales from ion channels in cells to organ systems \cite{scanziani2009electrophysiology}. Electrical signaling in the heart has vital functions related to intra and extracellular communication, rhythmicity of heartbeats, and provides a driving force for contraction. The action potential (AP) is the net transmembrane potential varying over time which results from the composite activities of different ion channels \cite{grant2009cardiac}. Fig~\ref{fig1}-(a) shows the simulated AP of a mouse ventricular apex myocyte using models adopted from \cite{bondarenko2004computer}. The AP is the result of orchestrated activities of various ionic currents described in Fig 1-(b). Even small changes in VGIC function can contribute to aberrant AP waveform and/or conduction, leading to arrhythmias. As illustrated in Fig~\ref{fig2}, $\text{Na}^{+}$ channels ($\text{Na}_{v}$) are responsible for AP initiation, or the depolarization phase, $\text{Ca}^{2+}$ channels ($\text{Ca}_{v}$) drive the prolonged depolarization phase particularly in larger species (“plateau”), while several $\text{K}^{+}$ channel ($\text{K}_{v}$) isoforms are collectively responsible for AP deactivation, i.e., repolarization. Like most transmembrane proteins, VGICs are heavily glycosylated membrane proteins \cite{ednie2011modulation}. Studies have proven that glycosylation can affect VGIC function predominantly. For example, we reported that a saturating, electrostatic effect of negatively charged sialic acids, which are typically attached to the terminal of glycan branches, significantly altered cardiac electrical signaling \cite{ednie2013expression, ednie2015reduced}. Our recent studies observed aberrant electrical signaling, e.g., prolonged APs and abnormal early re-activations, in Mgat1KO ventricular apex myocytes \cite{ednie2019reduced, ednie2019reduced2}. These observations strongly support direct and disease-related effects of reduced N-glycosylation on VGIC gating and activity.

@@

Therefore, this paper presents simulation modeling of dominant $\text{K}^{+}$ currents in mouse ventricular myocytes and further calibrate their parameters using the in-vitro data under normal and reduced glycosylation conditions through ablation of the Mgat1 gene. Specifically, we propose an optimization procedure to calibrate simulation models of potassium channel isoform activity, $\text{I}_{Kto}$ and $\text{I}_{Kslow}$, in mouse cardiomyocytes.  Fig 3 shows  major component $\text{K}^{+}$ currents, including $\text{I}_{Ksum}$, $\text{I}_{Kto}$, $\text{I}_{Kslow}$ and $\text{I}_{Kss}$. Key statistics of component currents, amplitudes, and inactivation rates ($\tau$'s) are measured from in-vitro experimental data with a 4.5 s voltage-clamp protocol (see details in Section III). The major contributions of this paper are summarized as follows.
\begin{itemize}
    \item Simulation models are integrated with in-vitro experiments to investigate the effects of reduced N-glycosylation on $\text{K}_{v}$ activity of mouse myocytes. Computer simulation helps demonstrate the voltage-gating mechanism and conductance kinetics that cannot be readily available through traditional exponential fitting. 
    \item A self-breeding Genetic Algorithm procedure is developed to calibrate simulation models of voltage-gated $\text{K}^{+}$ channel of mouse ventricular apex myocytes based on key characterisitcs and raw data obtained from in-vitro experiments.
    \item Calibrated models facilitate the prediction of $\text{K}_{v}$ characteristics at different voltages that are not observed in the in-vitro experiments. In the Mgat1KO group, both $\text{I}_{Kto}$ and $\text{I}_{Kslow}$ densities are shown to be significantly reduced and the rate of $\text{I}_{Kslow}$ inactivation is much slower.
    \item Simulation modeling of cardiac myocytes is conducive to gain a better understanding of detailed $\text{K}_{v}$ kinetics, as well as how reduced glycosylation through ablation of Mgat1 gene impacts $\text{K}_{v}$ kinetics.
\end{itemize}

\section*{Background}
% === II. RESEARCH BACKGROUND ===========================================
% =======================================================================
\subsection*{Glycosylation and DCM}
Protein glycosylation is an essential cellular process that impacts many cell functions \cite{marques2017cardiac}. Briefly, protein glycosylation is the sequential co-/post-translational process of attaching sugar residues (glycans) to proteins. Cardiac VGICs are heavily glycosylated proteins with upwards of 30\% of their mass consisting of N- and O-linked glycans. A growing number of cardiac diseases, including DCM and hypertrophic cardiomyopathy, can present with concurrent, albeit, modest changes in glycosylation \cite{gehrmann2003cardiomyopathy, footitt2009cardiomyopathy, marques2017cardiac}. Mgat1 expression was implicated in cardiac function and shown to be down-regulated in human end-stage idiopathic DCM. Genome-wide searches identified changes in glycosylation-related gene expression in human idiopathic DCM, including glycosyltransferases \cite{barrans2002global, hwang2002microarray, yung2004gene}; and proteomic/glycomic studies show changes in serum N-glycosylation in heart disease models and in humans with DCM risk factors \cite{nishio1995identification, knezevic2009variability, miura2016glycomics, nagai2016aberrant, yang2015glycoproteins}. Models of DCM/heart failure were associated with subtle changes in glycosylation of proteins involved in electromechanical processes, and ~20\% of patients with congenital disorders of glycosylation (CDG) present with cardiac deficits, including idiopathic DCM \cite{gehrmann2003cardiomyopathy, marques2017cardiac}. The data suggest a correlation between modest changes in extracellularly facing glycosylation and DCM/heart disease.

\subsection*{Simulation Modeling of Mouse Ventricular Myocytes}
Electrophysiology was pioneered by Hodgkin and Huxley with a series of well-known experiments on the squid giant axon \cite{hodgkin1952quantitative}. Their simulation model was built upon two fundamental principles observed in the experimental data. 1) Cells are selectively activated by different ion channels. 2) Activities of ion channels to produce ionic currents are controlled through voltage changes, from which the name ``voltage-gated ion channels'' originates. The voltage-gating mechanism is encoded in the simulations model with partial differential equations. Not only are simulation models compatible with data and descriptive, but they also simulate changes of AP waveforms and ion channel activity. Thus, models provide connections among ionic currents, action potentials, and disease effects. However, significant domain knowledge and in-vitro investigations are required, because simulation models often have complex structures based on nonlinear functions and differential equations with a high-dimensional set of parameters.

@@

\subsection*{$\text{K}_{v}$ Isoforms}
The orchestrated activity of different $\text{K}_{v}$ isoforms produces multiple component currents, as illustrated in Fig 1-(b) and Fig 3. However, it is difficult to rigorously delineate the multiple component $\text{K}^{+}$ currents through voltage-clamp experiments alone because only the sum of $\text{K}^{+}$ currents is measured and recorded. Thus, $\text{I}_{Ksum}$ is usually decomposed mathematically by fitting the peak and decaying portion of each component current trace with an exponential function \cite{brunet2004heterogeneous}. As given in Eq (1), a standard exponential function has three parameters: amplitude ($\text{A}$), time constant ($\tau$), and constant offset value $\text{C}$. $t$ is time in millisecond. Amplitude refers to the value of the peak and $\tau$ to the time constant when current reduces by $e^{-1}$ (~63\%) of the peak.
